---
title: "QMM PROBLEM 2"
author: "SRIKANTH CHETLAPALLY"
date: "2023-09-11"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

ASSIGNMENT 1 PROBLEM 2

**LP MODEL**

The Weigelt Corporation has three branch plants with excess production capacity.
Fortunately, the corporation has a new product ready to begin production, and all three
plants have this capability, so some of the excess capacity can be used in this way. This
product can be made in three sizes--large, medium, and small--that yield a net unit profit
of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to
produce 750, 900, and 450 units per day of this product, respectively, regardless of the
size or combination of sizes involved.
The amount of available in-process storage space also imposes a limitation on the
production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000
square feet, respectively, of in-process storage space available for a day's production of
this product. Each unit of the large, medium, and small sizes produced per day requires
20, 15, and 12 square feet, respectively.
Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large,
medium, and small sizes, respectively, would be sold per day.
At each plant, some employees will need to be laid off unless most of the plant’s
excess production capacity can be used to produce the new product. To avoid layoffs if
possible, management has decided that the plants should use the same percentage of their
excess capacity to produce the new product.
Management wishes to know how much of each of the sizes should be produced
by each of the plants to maximize profit.
a. Define the decision variables
b. Formulate a linear programming model for this problem

```{r}
table=matrix(c(420,750,13000,20,900,360,900,12000,15,1200,300,450,5000,12,750),ncol=5, byrow=T)
colnames(table)=c('PROFIT','EXCESS CAP','STORAGE','UNIT','SALES')
rownames(table)=c('large','medium','small')
table
```

PROFIT EXCESS CAP STORAGE UNIT SALES
large     420        750   13000   20   900
medium    360        900   12000   15  1200
small     300        450    5000   12   750

1.Define the decision variable
2.Linear a linear programming model for this problem

Anwser:

No of large units produced at plant1: D_l1
No of medium units produced at plant1: D_m1
No of small units produced at plant1: D_s1
No of large units produced at plant1: D_l2
No of medium units produced at plant1: D_m2
No of small units produced at plant1: D_s2
No of large units produced at plant1: D_l3
No of medium units produced at plant1: D_m3
No of small units produced at plant1: D_s3

O
bjective function:

$$ MAX \hspace{.3cm} Z = 420(D_l1+D_m2+D_s3)+360(D_l1+D_m2+D_s3)+300(D_l1+D_m2+D_s3)$$

Constraints

Production capacity constraints:

The production of each size at each plant should not exceed the respective plants capacity
excess capacity for each plant is 750, 900 and 400 units per day.

$$D_l1+D_m1+D_s1 \le 750$$

$$D_l2+D_m2+D_s2 \le 900$$

$$D_l3+D_m3+D_s3 \le 450$$

Storage space restrictions at present: the production of ecah size at each plant should not exceed the available in process storage space



$$20D_l1+15D_m1+12D_s1 \le 13000$$

$$20D_l2+15D_m2+12D_s2 \le 12000$$

$$20D_l3+15D_m3+12D_s3 \le 5000$$

Demand constraint:

The production of each size meet the scale forecast.

$$D_l1+D_m1+D_s1 \le 900$$

$$D_l2+D_m2+D_12 \le 1200$$

$$D_l3+D_m3+D_s3 \le 750$$

Restrictions on layoffs of employees:

$$(D_l1+D_m1+D_s1)/750 = (D_l2+D_m2+D_s2)/900 = (D_l3+D_m3+D_s3)/450$$

Non negativity constraints:

$$Dl>0,Dm > 0,Ds > 0$$




























